---
title: "Introduction to Hypothesis Testing"
teaching: 45
exercises: 10
---

:::::::::::::::::::::::::::::::::::::: questions

- What are inferential statistics?
- What is a hypothesis?
- How can I test a hypothesis?

::::::::::::::::::::::::::::::::::::::::::::::::
  
::::::::::::::::::::::::::::::::::::: objectives

- Define a null and alternative hypothesis
- Understand the hypothesis-testing process
- Recognise the different types of hypothesis testing errors

::::::::::::::::::::::::::::::::::::::::::::::::

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hypothesis Testing

The following is a well-established research pipeline: 
1. Define a research question, or hypothesis
2. Design an appropriate study or trial to test that hypothesis
3. Conduct the study or trial
4. Observe, collate and process the results (data)
5. Measure the agreement with the hypothesis
6. Draw conclusions regarding the hypothesis

In this model, the hypothesis should be clearly defined and testable. In
hypothesis testing, this means that our question has just two possible answers:
a ”null hypothesis” (H<sub>0</sub>), which is a specific statement that we are 
looking to disprove with our data, and an “alternative hypothesis” 
(H<sub>1</sub>), which is a statement opposing H<sub>0</sub> and which we will 
only accept if the data and analysis is sufficiently convincing.

::::::::::::::::::::::::::: tip

## Tip: Defining your alternative hypothesis
The alternative hypothesis must cover all options not included in the null
hypothesis; if H<sub>0</sub> is: “There is no difference between A and B”, 
then H<sub>1</sub> must be: “A and B are different”, not: “A is greater than
B”. Generally, a two-sided test (“A and B are different”) is regarded as
better practice than a one-sided test (“A is greater than B”).

::::::::::::::::::::::::::::



::::::::::::::::::::::::::::::::::::: challenge 

## Challenge 1

Imagine you were testing a new medical treatment. What might be the most
appropriate null and alternative hypotheses?
1. Null – the new treatment is worse than the existing treatment. Alternative
– the new treatment is better than the existing treatment
2. Null – there is no difference between the new and old treatments.
Alternative – there is a difference between the new and existing treatments
3. Null – there is a difference between the new and existing treatments.
Alternative – there is no difference between the new and existing treatments
4. Null – there is no difference between the new and old treatments.
Alternative – the new treatment is better than the existing treatment

::::::::::::::::::::::::::::::::::::: solution

## Solution to challenge 1
Option 2 is the correct answer - the default assumption (the null
hypothesis) is that there is no difference between the two treatments, and
we need convincing evidence to accept that the new treatment has a different
outcome (the alternative hypothesis). Think about why the other options may
not be suitable. Can you come up with another valid null and alternative
hypothesis?

:::::::::::::::::::::::::::::::::::::  
:::::::::::::::::::::::::::::::::::::  





## Introduction

This is a lesson created via The Carpentries Workbench. It is written in
[Pandoc-flavored Markdown](https://pandoc.org/MANUAL.txt) for static files and
[R Markdown][r-markdown] for dynamic files that can render code into output. 
Please refer to the [Introduction to The Carpentries 
Workbench](https://carpentries.github.io/sandpaper-docs/) for full documentation.

What you need to know is that there are three sections required for a valid
Carpentries lesson template:

 1. `questions` are displayed at the beginning of the episode to prime the
    learner for the content.
 2. `objectives` are the learning objectives for an episode displayed with
    the questions.
 3. `keypoints` are displayed at the end of the episode to reinforce the
    objectives.

:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::: instructor

Inline instructor notes can help inform instructors of timing challenges
associated with the lessons. They appear in the "Instructor View"

::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: challenge 

## Challenge 1: Can you do it?

What is the output of this command?

```r
paste("This", "new", "lesson", "looks", "good")
```

:::::::::::::::::::::::: solution 

## Output
 
```output
[1] "This new lesson looks good"
```

:::::::::::::::::::::::::::::::::


## Challenge 2: how do you nest solutions within challenge blocks?

:::::::::::::::::::::::: solution 

You can add a line with at least three colons and a `solution` tag.

:::::::::::::::::::::::::::::::::
::::::::::::::::::::::::::::::::::::::::::::::::

## Figures

You can also include figures generated from R Markdown:

```{r pyramid, fig.alt = "pie chart illusion of a pyramid", fig.cap = "Sun arise each and every morning"}
pie(
  c(Sky = 78, "Sunny side of pyramid" = 17, "Shady side of pyramid" = 5), 
  init.angle = 315, 
  col = c("deepskyblue", "yellow", "yellow3"), 
  border = FALSE
)
```

Or you can use standard markdown for static figures with the following syntax:

`![optional caption that appears below the figure](figure url){alt='alt text for
accessibility purposes'}`

![You belong in The Carpentries!](https://raw.githubusercontent.com/carpentries/logo/master/Badge_Carpentries.svg){alt='Blue Carpentries hex person logo with no text.'}

## Math

One of our episodes contains $\LaTeX$ equations when describing how to create
dynamic reports with {knitr}, so we now use mathjax to describe this:

`$\alpha = \dfrac{1}{(1 - \beta)^2}$` becomes: $\alpha = \dfrac{1}{(1 - \beta)^2}$

Cool, right?


:::::::::::::::::::::::::::::::::::: keypoints

- Select appropriate and testable null and alternative hypotheses
- Interpret p-values and statistical significance correctly

:::::::::::::::::::::::::::::::::::: 

[r-markdown]: https://rmarkdown.rstudio.com/